Storing messages with multipartite neural cliques

### 2014-07-07 Articles/article.tex
...

\usepackage[english]{babel} 
\usepackage[T1]{fontenc}
%\usepackage{fullpage}
\usepackage[]{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
%\usepackage{pstricks}
\usepackage{float}
\usepackage[autolanguage]{numprint}
\usepackage[affil-it]{authblk}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%
%\usepackage[style=numeric,backend=bibtex]{biblatex}
\pagestyle{myheadings}

@@

		$w = a$	is optimal

@@

	$\eta_m = (P_{retrieve} m ) \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)}$
	%\frac{c}{(c-c_e) \log_2{l \choose a }}

>>>>

\usepackage[english]{babel} 
\usepackage[T1]{fontenc}
%\usepackage{fullpage}
\usepackage[]{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
%\usepackage{pstricks}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[autolanguage]{numprint}
\usepackage[affil-it]{authblk}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%
%\usepackage[style=numeric,backend=bibtex]{biblatex}
\pagestyle{myheadings}

@@

		$w = a$	is optimal
		\begin{algorithm}
		\caption{$a$-sum of sum}
		\label{asumsum}
		\begin{algorithmic}
		\Require{}
		\Statex
		\While{step < I}
		\If {$i\geq maxval$}
   	 	\State $i\gets 0$
		\Else
    		\If {$i+k\leq maxval$}
        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
    		\EndIf
		\EndIf
		\EndWhile
		\end{algorithmic}
		\end{algorithm}

@@

	We define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory). A perfect associative memory would use exactly the same number of bits than the original messages and recover messages by maximum likelihood (ambiguities causing errors). Efficiency is the amount of information retrieved divided by the hardness of the problem.

	$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)}$
	%\frac{c}{(c-c_e) \log_2{l \choose a }}
